Lonely and online: an investigation of social media use and social isolation in China

### 2024-06-10 tandf/Response to reviewers jg revised.qmd

*6.	Reference is needed in the first sentence of the second paragraph in the Literature Review and Theory section.*

The references for this claim was located at the end of the paragraph where the arguments of the authors were described in detail. Though, we can see how it would be confusing. We moved the references to the end of the first sentence.

*7.	Nothing in the literature review about social media addiction. I suggest to see: Social isolation, social support and their relationship with smartphone addiction; examples: The relationship between addiction to smartphone usage and depression among adults: A crosssectional study, Smartphone addiction among university students in the light of some variables, and Examining the effects of motives and gender differences on smartphone addiction.*

We agree that smartphone addiction, depression, and feelings of loneliness and a sense of isolation may be related.These works have been added to the literature review.

@@

*9.	Also, a clear research question need to be stated in the end of the introduction section.*

We re-wrote the second half of the introduction to clarify our research question and contribution.

*10.	How can the researchers explain that the sample represent ALL China? We know the cultural diversity in a “BIG” China.*

We added more details about the sampling strategy in the introduction of the data and measurement section to better explain the strengths and weaknesses of our data when it comes to their external validity.

@@

*11.	Need more explanation about the sample. Researchers stated it is random sample. How? Clarification is needed.*

See point 10.

*12.	I suggest that the method section needs to start with sample.*

The first paragraph of the methods section now addresses the sample in more detail.

@@

*13.	No need for the margin in the end of page 5. This information is vital and essential procedures. Need to be moved in the body of the research.*

We are not sure to exactly what the reviewer is referring here. We think the reference is to the footnote at the end of page 5, and there's a typo in the reviewer's comment ("margin" should be "footnote"). We assumed this was the case. If so, we decided to leave the footnote as is. Because we added more description of the sample in the main body of the text, and the footnote draws attention to the fact that the adjustments we made were not related to the indicators used in the present studies, we thought it would unnecessarily interrupt the flow of the text.

*14.	Validity and reliability are needed for the measurements.*

We included the alpha statistic for the dependent variable; it is high at 0.86. We also added the reliability estimate for social media use. It was not high ($\alpha = 0.31$) but we moved forward with the index because the face validity is pretty clear, those who claim to use social media generally more often, claim to read political news more often, and claim to use it more than they did in the past, are likely to be more frequent social media users than those who do not do these things. Also we added confirmation to the measurement description that the three social media use items were all positively correlated with each other (p < 0.0001 for all pairwise relationships).

*15.	Figure ?? and Table ?? are  noticed. Need to number the figures and tables.*

### 2024-06-10 tandf/Social Isolation in China jg revised.qmd
updated files from jg

This study uses the little-studied Chinese social media environment to answer two research questions that remain unresolved in the literature: 1) through which channels or mechanisms do possible heterogeneous effects operate through and 2) how much does internet context change the relationship between social isolation and social media use. The reason that we believe the case of China can be helpful in answering these question is that Chinese online environment has certain features that should both moderate and exacerbate key causal pathways previously identified in the literature. To resolve these debates, we employ a large survey (n=2292) of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is generally negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship. These results are consistent with a mechanism that links the two via the harmfulness of being exposed to constant online comparisons (so-called FOMO or fear of missing out). However, the contextual differences of the Chinese internet compared to the Western intern do not appear to significantly alter the relationship.

@@

The data used in this study are original. We designed a survey instrument in English, and translated it into Chinese, to measure a range of concepts including social isolationism and various dimensions of social media and digital information consumption. We employed Qualtrics to collect the data. They randomly selected 2292 respondents from their existing panel[^2] from November 25 to December 2, 2015. This sample size on provides for a roughly $\pm2$ margin of error.[^3]

@@

@@

We measured general social media use with an index based on the following three items: 1) About how many hours a day would you estimate you spend using only social media? Social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other. (0-1, 1-2, 2-3, 3-4, 4-5, 5-6, 6-7, 7-8, 8-9, or More than 9), 2) Do you check email, read websites, and use social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other) more than you did five years ago? (Yes, No), and 3) How often do you read news stories about political events that have been posted on social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other)? (More than once a day, Everyday, Three-to-five days per week, One-to-two days per week, Less often, Never). Each was recoded so that higher values represented more social media use, rescaled to range from 0 through 1, added together, and then again, rescaled to range from 0 through 1 maintaining all original intervals. The distribution of this index is presented in @fig-sm-use-dist. The distribution is relatively normal and tightly centered around the mean 0.63 with a standard deviation of 0.17, but there is a left skew suggesting that a portion of the population is not that social media active, but clearly the bulk of the population are.

>>>>

This study uses the little-studied Chinese social media environment to answer two research questions that remain unresolved in the literature: 1) through which channels or mechanisms do possible heterogeneous effects operate through and 2) how much does internet context change the relationship between social isolation and social media use. The reason that we believe the case of China can be helpful in answering these question is that Chinese online environment has certain features that should both moderate and exacerbate key causal pathways previously identified in the literature. To resolve these debates, we employ a large survey (n=2292) of Chinese internet users and test a variety of regression specifications.[^1] The main result is that social media use is generally negatively related to social isolation, though the nature of this relationship changes depending on the urbanicity of the respondent - being in a rural area amplifies this relationship. These results are consistent with a mechanism that links the two via the harmfulness of being exposed to constant online comparisons (so-called FOMO or fear of missing out). However, the contextual differences of the Chinese internet compared to the Western internet do not appear to significantly alter the relationship.

@@

The data used in this study are original. We designed a survey instrument in English, and translated it into Chinese, to measure a range of concepts including social isolationism and various dimensions of social media and digital information consumption. We employed Qualtrics to collect the data. They randomly selected 2292 respondents from their existing panel[^2] from November 25 to December 2, 2015. This sample size on provides for a roughly $\pm2$ margin of error.[^3] While our sample is selected randomly from Qualtrics' online user panel, it isn't representative of China's entire population due to its internet-based recruitment methods. The sample, however, aligns well with Chinese internet users, crucial for our internet effects research. Compared to national data, our sample skews younger and more educated but is similar in income and gender.[^4] These demographics reflect the global digital divide and are in line with expectations for internet users in developing regions. Our findings are particularly relevant for understanding digital media's impact among active internet users in China.

@@

[^4]: See https://data.worldbank.org/country/china (go to the Country Profile), and https://www.cnnic.com.cn/AU/Introduction/Introduction/201208/t20120815_33295.htm.

@@

We measured general social media use with an index based on the following three items: 1) About how many hours a day would you estimate you spend using only social media? Social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other. (0-1, 1-2, 2-3, 3-4, 4-5, 5-6, 6-7, 7-8, 8-9, or More than 9), 2) Do you check email, read websites, and use social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other) more than you did five years ago? (Yes, No), and 3) How often do you read news stories about political events that have been posted on social media (social media means applications like Weibo, QQ, Renren, Kaixin001, Douban, WeChat or other sites and services that allow users to interact with each other)? (More than once a day, Everyday, Three-to-five days per week, One-to-two days per week, Less often, Never). Each was recoded so that higher values represented more social media use, rescaled to range from 0 through 1, added together, and then again, rescaled to range from 0 through 1 maintaining all original intervals.The Chronbach's alpha was relatively low for these three items ($\alpha = 0.31$), but we proceeded with the construction of this index because, first, the face validity is high. Simply, those who claim to use social media generally more often, claim to read political news more often, and claim to use it more than they did in the past, are certainly likely to be more frequent social media users than those who do not do all these things.Second, we confirmed that these three items were all positively correlated with each other (p < 0.0001 for all pairwise relationships). The distribution of this index is presented in @fig-sm-use-dist. The distribution is relatively normal and tightly centered around the mean 0.63 with a standard deviation of 0.17, but there is a left skew suggesting that a portion of the population is not that social media active, but clearly the bulk of the population are.
